---
title: "DATA 205: Montgomery County Tuition"
author: "Jeremy Yee"
date: "2/11/2022"
output: html_document
---

### Exploratory Data Analysis of Tuition in Montgomery County

### Dataset
Data Montgomery: https://data.montgomerycountymd.gov/Education/Tuition-Assistance/p7z5-tjrz

This dataset includes a list of classes approved and paid through the County tuition assistance program. Update Frequency: Twice a Year

### Data Description

The dataset consist of around 3,870 rows and 7 columns.

#### Department
* Name of the County Department to which the Employee is assigned

#### Major
* Name of a Major to which employee is currently pursuing

#### Degree
* Name of a Degree Program to which the employee is currently enrolled

#### School
* Name of a school/institution where employee took the course(s)

#### Course Title
* Name of a course/seminar/conference taken by the employee

#### Course Description 
* Brief description of the course/seminar/conference taken by the employee

#### Cost
* Amount of financial aid paid through the County tuition assistance program

### Required Libraries
```{r}
library(tidyverse)
library(ggplot2)
library("knitr")
library(dplyr)
```

### Data Preparation
```{r}
# Setting working directory
setwd("C:/Users/Jerem/OneDrive/Documents")
# Provide a fast and friendly way to read rectangular data
library(readr)
# rereading dataset into bees
Tuition <- read_csv("Montgomery College/Spring 2022/DATA 205/Datasets/Tuition_Assistance.csv")
#View(Tuition)
```

```{r}
str(Tuition)
```

### Data Cleaning 
Data is too complex and would interfere with the exporation. Therefore removed from the dataset.
```{r}
# Removing variables from the dataset
Tuition$`Course Description` = NULL
```

There are 341 unique values in the School column. 
```{r}
unique(Tuition$School)
```

Due to the time limit and cleaning, this exploration is going to focus on one unique value. Since DATA 205 is a Montgomery College course, data is focus on Montgomery College.
```{r}
# Subsetting variable
MC_Tuition <- subset(Tuition, Tuition$School == "Montgomery College Rockville Campus")
```

### Dataframe
```{r}
MC_Tuition %>% head() %>% knitr::kable()
```

The new dataframe consist of 215 rows and 6 columns.

### EDA
```{r}
# Barplot of MC Departments
ggplot(MC_Tuition, aes(x = Department, y = Cost, fill = Department)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  theme(legend.position = "none") +
  labs(title = "Tuition Towards MC Departments",
       x = "Departments",
       y = "Cost (USD)")
```

The department of General Service has the highest tuition.

```{r}
# Barplot of MC Majors
ggplot(MC_Tuition, aes(x = Major, y = Cost, fill = Major)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  theme(legend.position = "none") +
  labs(title = "Tuition Towards each Major",
       x = "Major",
       y = "Cost (USD)")

```

Business/Admin./Mgmt. majors are the most likey to earn a higher tuition according to the data. But this can also mean that majority of the school body is Business/Admin./Mgmt. majors.

```{r}
# Barplot of MC Degree
ggplot(MC_Tuition, aes(x = Degree, y = Cost, fill = Degree)) +
  geom_bar(stat = 'identity') +
  theme(legend.position = "none") +
  labs(title = "Tuition Towards MC Degree",
       x = "Degree",
       y = "Cost (USD)")
```

Majority of the tuition is towards an Assoicates degree. This is because Montgomery College's academic program usually prepare students to earn an associates degree so they can transfer to a four year college. 